\documentclass{../../cls/cv}

\renewcommand{\categoryfont}{\sc}

%
% set the space used for category titles here:
% use the same value for oddsidemargin and marginparwidth [the latter
% 		will be reset to account for marginparsep]
%
\setlength{\oddsidemargin}{0.75in}
\setlength{\marginparwidth}{1.1in}
%
% calculate other dimensions [textwidth and evensidemargin]
% in function of oddsidemargin and marginparwidth:
% would be nicer to put in the class file...
%
\addtolength{\marginparwidth}{-\marginparsep}
 \setlength{\evensidemargin}{\oddsidemargin}
 \setlength{\textwidth}{\paperwidth}
 \addtolength{\textwidth}{-2in}
 \addtolength{\textwidth}{-2\oddsidemargin}
 \addtolength{\textwidth}{\marginparwidth}
 \addtolength{\textwidth}{\marginparsep}
%
%
\setlength{\topmargin}{-1.25in}
%
%
\renewcommand{\labelcitem}{$\diamond$}
\renewcommand{\labelitemi}{$\cdot$}
\newcommand{\first}{$1^{\mbox{\scriptsize st}}$\ }
\newcommand{\second}{$2^{\mbox{\scriptsize nd}}$\ }
\newcommand{\third}{$3^{\mbox{\scriptsize rd}}$\ }

%\selectlanguage{swedish}
%\selectlanguage{english}
\usepackage[gen]{eurosym}

\author{Samuel Gabrielsson - Curriculum Vitae}
% ------ Address ----------------------------------------------------

\address{Johannesgatan 6 lgh 1001 \\
	111 38 Stockholm \\
	Sweden \\
	\ \\
	Phone: +46 (0)1 071 57192 \\
	Mobile: +46 (0)72 724 21 92 \\
	\mbox{\small\tt Email: samuel.gabrielsson@gmail.com }}
% ------ End Address ----------------------------------------------------

\begin{document}
\maketitle

% -------- Work experience ------------------------------------
\begin{category}{Work \\experience}
\citem{Software Developer and Team Leader}, Ericsson AB, Radio Software Department, Kista, Sweden. (June 2011 -- Ongoing).
\begin{itemize}
   \item Lead a software team focusing on the driver parts of the radio.
   \item Write drivers for RBS 6000 hardware which supports GSM/EDGE, WCDMA/HSPA and LTE.
   \item Research and pre-develop next generation radio platform. Replace the operating system OSE with Linux.
   \item Short term assignment (3 months) in Ottawa as a software/hardware integrator for AIR 32.
\end{itemize}

\citem{Ericsson AB} Combitech consultant at Linux Center, \"Alvsj\"o, Sweden. (August 2008 -- May 2011).\\
Software Developer (May 2010 -- May 2011).
\begin{itemize}
   \item Develop kernel patches and test Ericsson product ENUX. ENUX is a GNU Linux Embedded operating system used by a Virtual Machine to emulate APZ classic run time environment for PLEX based programs such as AXE.
   \item Designer and tester for other Ericsson products such as CPBS, GSDI and IS.
\end{itemize}
Automated Function Tester (August 2008 -- April 2010).
\begin{itemize}
   \item Framework developer for automated test cases.
   \item Develop automated test cases for Ericsson products Linux Opensource Telecom Cluster (LOTC) and SLES Virtual Platform (SVP) based on Xen.
   \item Open Multimedia Platform (OMP) customer forum support.
   \item Handle and solve trouble reports for all the products.
\end{itemize}

%\citem{Systems Engineering Consultant}, Combitech AB (August 2008 -- May 2011).

\citem{Mail Carrier}, City-Mail Sweden AB (June 2000 -- August 2001, Summers 2002 -- 2005).
\begin{itemize}
   \item Sorting and distribution.
   \item Updating the computer-based estate register.
\end{itemize}

\citem{Substitute Teacher}, S\"odert\"alje Municipality (Fall 1999 --
Spring 2000). \\
Teaching junior high school students math, chemistry and physics.

\citem{Military Service}, KA1 Waxholm (January 1999 -- October 1999).
%\begin{itemize}
%   \item The royal guards at the royal palace in Stockholm and security guard.
%   \item Leadership experience and basic medical education.
%   \item Handle technical equipment for advanced management.
%\end{itemize}
\end{category}

% ------- Education --------------------------------------------------
\begin{category}{Education}
\citem{Lule\aa\ University of Technology}, Sweden (August 2001 -- May 2008).\\
M.Sc. in computer science specializing in applied mathematics.

\citem{University of Toronto}, ON, Canada (August 2006 -- July 2007). \\
Research assistant for professor J. Christopher Beck.
\begin{itemize}
   \item Research in artificial intelligence and planning.
   \item Research in optimization, parallel and distributed algorithms and communications protocol.
   \item Cluster setup and maintenance.
\end{itemize}

\citem{V\"asterg\aa rd High School}, S\"odert\"alje, Sweden.\\
Natural science programme (August 1995 -- June 1998).
\end{category}

% -------- Publications ------------------------------------
\begin{category}{Publications}
\citembullet ``A Parallel Tabu Search Algorithm for the Quadratic Assignment Problem'', Masters thesis, Lule\aa\ University of Technology, Sweden (September 2007).
\citembullet ``Solving Combinatorial Problems with Parallel Cooperative Solvers'', Ninth International
Workshop on Distributed Constraint Reasoning, Brown University Providence, Rhode Island, USA (July 2007).
\end{category}

% -------- Research \\ Projects ------------------------------------
\begin{category}{Research \\ Projects}
\citembullet ``Modelling Security Protocol Synthesis with AI Planning'', University of Toronto, ON, Canada (December 2006).
\citembullet ``Density Functional Theory and a Simulation of Water Absorption on a Germanium Surface'', Lule\aa\ University of Technology, Sweden (March 2005).
\end{category}


%-------- Activities --------------------------------------------------
\begin{category}{Activities}
\citem{Committee Member}, Lule\aa \ University Academic
Computer Society (2005 -- 2006).
\citem{Treasurer}, Lule\aa \ University Academic Computer Society
(2004 -- 2005).
\begin{itemize}
\item About $600$ registered student members.
\item Responsible for a budget of over 180 000 kr (\euro18 000).
\end{itemize}
\end{category}

% ------- Skills ------------------------------------------------------
\begin{category}{Skills}
\citembullet Bash, C/C++, CSS, Expect, Haskell, HTML, Java, \LaTeX, Lisp/Scheme, Maple, Matlab,
Mips32, MPI (OpenMPI, MPICH2), Pascal, Perl, PHP, Python, Ruby, SQL, Tcl.
\citembullet Maui Cluster Scheduler, PSpice, Red Hat crash analysis utility, TORQUE Resource Manager.
\citembullet ClearCase, CVS, Gerrit, Git, Jenkins, SVN
\citembullet GNU Linux (from scratch), OSE, Solaris, Open-BSD, Free-BSD, Be-OS, MS-DOS, MS-Windows.
\citembullet Fluent spoken/written Swedish, English, Syriac Aramaic;
fair German; \\ beginner Chinese-Mandarin.
\end{category}

% -------- Hobbies --------------------------------------------
%\begin{category}{Hobbies}
%\citemnobullet CrossFit, Indoor (floor) Hockey, Table Tennis
%\end{category}

% -------- Reference --------------------------------------------

\begin{category}{References}
\citemnobullet Will be supplied on request.
%\citem{Vice-chancellor Inge S\"oderkvist} (Thesis supervisor) \\
%Lule\aa\ University of Technology \\
%Department of Mathematics \\
%S-97187 Lule\aa, Sweden \\
%\ \\
%Phone: +46 (0)920 492130 \\
%Fax: +46 (0)920 491073 \\
%Email: inge@sm.luth.se \\
%Web site: http://www.ltu.se/staff/i/ingsor

%\citem{Professor J. Christopher Beck} \\
%University of Toronto \\
%Department of Mechanical \& Industrial Engineering and \\
%Department of Computer Science \\
%5 King's College Rd. \\
%Toronto, ON M5S 3G8, Canada \\
%\ \\
%Phone: +1 416 946 8854 \\
%Fax: +1 416 878 7753 \\
%Email: jcb@mie.utoronto.ca \\
%Web site: http://www.mie.utoronto.ca/staff/profiles/beck
\end{category}

\end{document}
